### 2018-02-20 paper/algorithm.tex
changed participants names because I wanted to

\NewCryptoEntity{\Alice}{A}
\NewCryptoEntity{\Bob}{B}
\NewCryptoEntity{\Carol}{C}
\NewCryptoEntity{\David}{D}

We have several participants: Alice, Bob, Carol and David.
Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
  \David\}\)).
We have two protocols to track knowledge: one protocol which is run between the 
devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
swarm, and another run between different swarms (the Inter-Swarm Protocol) to 
keep global knowledge.
Finally, we have a file-sharing protocol which uses the local and global 
knowledges to coordinate file sharing between devices in different swarms.

@@

When Alice wants to transfer a file to Bob, she will find which devices have the 
file (from \(F_i\)), then predict when any of those devices will be available 
(from \(A_i\)).
Then she will construct a probabilistic onion route with her devices as the 
destinations.
She will encrypt this route for Bob and transfer it to him, who now can use the 
onion route to fetch the file.

>>>>

\NewCryptoEntity{\Alfred}{A}
\NewCryptoEntity{\Beth}{B}
\NewCryptoEntity{\Cathy}{C}
\NewCryptoEntity{\David}{D}

We have several participants: Alfred, Beth, Cathy and David.
Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alfred, \Beth, \Cathy, 
  \David\}\)).
We have two protocols to track knowledge: one protocol which is run between the 
devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
swarm, and another run between different swarms (the Inter-Swarm Protocol) to 
keep global knowledge.
Finally, we have a file-sharing protocol which uses the local and global 
knowledges to coordinate file sharing between devices in different swarms.

@@

When Alfred wants to transfer a file to Beth, she will find which devices have the 
file (from \(F_i\)), then predict when any of those devices will be available 
(from \(A_i\)).
Then she will construct a probabilistic onion route with her devices as the 
destinations.
She will encrypt this route for Beth and transfer it to him, who now can use the 
onion route to fetch the file.
